### 2011-05-05 paper/paper.tex
blah

\begin{theorem}[{\bf Hit-and-run bound}] Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$\displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the variation distance of the chain is within $\epsilon$ of the uniform distribution.
\end{theorem}
This bound is polynomial in $n$, so in theory, it is better than the Metropolis methods. The constant, however, is very larger, and so our hope is that, when tested in practice, the hit-and-run method will mix to the uniform distribution even faster than in the time given by this bound.

>>>>

\begin{theorem}[{\bf Hit-and-run bound}] Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $\sigma$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - \sigma(r)| \le \epsilon$.\end{center}
\end{theorem}

This bound is polynomial in $n$, so in theory, it is better than the Metropolis methods. The constant, however, is very larger, and so our hope is that, when tested in practice, the hit-and-run method will mix to the uniform distribution even faster than in the time given by this bound.
